Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-01-18 docs/msr.tex
more on the introduction.

A security-related bug is a programming error that introduces a potentially
exploitable weakness into a computer system. This weakness could lead to a
security breach with unfortunate consequences in different layers, like databases,
native code, applications, libraries and others. Despite the significant
effort to detect and eliminate such bugs, little attention has been paid to
study them in relation to software evolution.

One of the most common approaches to identify software vulnerabilities is {\it static analysis}.
This kind of analysis is performed by automated tools either on the program's source
or object code and without actually executing it.

>>>>

A security-related bug is a programming error that introduces a potentially
exploitable weakness into a computer system. This weakness could lead to a
security breach with unfortunate consequences in different layers, like databases,
native code, applications, libraries and others. Despite the significant
effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
study them in relation to software evolution~\cite{L96, LRWPT97}. In this paper we present how we
used a large software ecosystem to analyze how evolving software packages are
related to the different types of software vulnerabilities.

One of the most common approaches to identify software vulnerabilities is
{\it static analysis}~\cite{CW07}. This kind of analysis is performed by automated tools
either on the program's source or object code and without actually executing
it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
an effective static analysis tool that has already been used in
research~\cite{AP10, HP07}. Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the Maven repoistory (280GB of
data). Then we observed the changes that involved the security bugs per project
version.
